Rank Comparison

### 2024-11-29 Code/RankComparison.Rmd
Updated language and removed supplementary code

clusWilcox.test(Time, group=Year, cluster = Athlete, data = men_2019,
                method = "ds",
                exact = TRUE, B = 1000000)
```

@@

clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_2019,
                method = "ds",
                exact = TRUE, B = 1000000)
```

@@

@@

clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_2022,
                method = "ds",
                exact = TRUE, B = 1000000)
```

@@

@@

>>>>

clusWilcox.test(Time, group=Year, cluster = Athlete, data = men_2019,
                method = "ds",
                exact = TRUE, B = 1000000)
```
The p-value from the asymptomatic test was $1.126 \cdot 10^{-5}$ and the p-value
from the permutation test was $2.8 \cdot 10 ^ {-5}$. Both of these are
statistically significant results showing a difference in male athletes who
competed in 2019 and 2022.

@@

clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_2019,
                method = "ds",
                exact = TRUE, B = 1000000)
```
The p-value from the asymptomatic test was $6.9 \cdot 10^{-3}$ and the p-value
from the permutation test was $1.5 \cdot 10^{-3}$. Both of these are
statistically significant results showing a difference in female athletes who
competed in 2019 and 2022.

@@

The p-value from the asymptomatic test was $6.1 \cdot 10^{-5}$ and the p-value
from the permutation test was $1.0 \cdot 10^{-6}$. Both of these are
statistically significant results showing a difference in male athletes who
competed at various competitions in 2022.

@@

clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_2022,
                method = "ds",
                exact = TRUE, B = 1000000)
```
The p-value from the asymptomatic test was $1.2 \cdot 10^{-3}$ and the p-value
from the permutation test was $1.0 \cdot 10^{-6}$. Both of these are
statistically significant results showing a difference in female athletes who
competed at various competitions in 2022.

@@

The p-value from the asymptomatic test was $1.4 \cdot 10^{-6}$ and the p-value
from the permutation test was $2.8 \cdot 10 ^ {-5}$. Both of these are
statistically significant results showing a difference in male athletes who
competed in 2022 and 2023.

@@

The p-value from the asymptomatic test was $9.4 \cdot 10^{-7}$ and the p-value
from the permutation test was $1.5 \cdot 10^{-3}$. Both of these are
statistically significant results showing a difference in female athletes who
competed in 2019 and 2022.
